---
title: "CODA TMSR Report"
output: html_document
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
---

```{r setup, include=FALSE}
library(worcs)
library(dbscan)
library(umap)
library(data.table)
library(ggplot2)
library(reticulate)
library(targets)
#tar_config_set(store = "../_targets")
use_virtualenv("tmsrcoda")
knitr::opts_chunk$set(echo = FALSE)
fig_format = ".png"
```

```{r}
tar_load(df)
tar_load(exmplrs)
tar_load(res_hdbscan)
tab_clust <- table(res_hdbscan$labels)[names(exmplrs)]
```

# The Current Study

The current study seeks to generate a nomological net of the literature on human cooperation by means of a comprehensive text mining systematic review (TMSR).
This is an inductive study, and as such, does not test hypotheses [@wagenmakersCreativityVerificationCyclePsychological2018].
The aims of the study are to identify the relevant constructs in the body of literature and to map potential relationships between constructs based on their co-occurrence within studies.
The resulting graph provides a conceptual overview of this body of literature.
		
This text mining systematic review considered the *frequency* with which a construct is covered in the literature, or *term frequency*, to be indicative of its relevance.
Term frequency can be rank ordered to identify the most relevant constructs.
Furthermore, the frequency with which constructs are investigated together within publications, or *co-occurrence*, is considered to be indicative of a putative relationship between them.
These two metrics can be jointly visualized as a network,
thereby "mapping" constructs relevant to cooperation.

Inductive research affords the researcher with substantial creativity [@wagenmakersCreativityVerificationCyclePsychological2018].
This means that subjective decisions are made throughout the analysis process.
To ensure that all such decisions are properly documented,
all code, data, and the historical record of this project are available in a public research repository at [https://github.com/cjvanlissa/tmsr_coda](https://github.com/cjvanlissa/tmsr_coda). 
The Workflow for Open Reproducible Code in Science was used to make all analyses reproducible [WORCS, @vanlissaWORCSWorkflowOpen2020].
Reuse of the analysis code and secondary analysis of the data are encouraged.

# Methods

## Data Cleaning

The original corpus consisted of 2195 abstracts of papers included in the Cooperation Databank as of DATE.
We first removed missing abstracts, those shorter than 200 characters (approximately 30 words), those not formatted as plain text, and those not written in English.
The remaining plain-text abstracts were further preprocessed by removing HTML tags, email addresses, control characters, ligatures, initials, punctuation, and numbers. 
As we observed some concatenated sentences, we used the `wordninja` package to extract individual words from any string exceeding a length of 15 characters.
Finally, we normalized spacing throughout the abstracts.
After cleaning, we included words from 1880 abstracts.

## Vector Embedding

Our analysis focused on nouns and adjectives, as these are (jointly) able to represent constructs.
Nouns most commonly reference theoretically meaningful constructs; for example, the words "prisoner's dilemma" will both be tagged as nouns.
However, adjectives occasionally also capture meaningful constructs; for example, the words "competitive individuals" will be tagged as an adjective and a noun. In this case, the word "individuals" does not relate to a theoretically meaningful construct, but the adjective "competitive" does.
We performed Part-Of-Speech (POS) tagging using the `stanza` pipeline to identify nouns and adjectives; henceforth referred to jointly as words.
We obtained numerical representations for the words using the pretrained SciBERT language model.
This model is finetuned on scientific text data, including studies of cooperation, and should thus provide high quality context-aware numerical representations.
Moreover, SciBERT and other BERT models are able to handle words that did not occur in the training vocabulary, thus allowing a complete-data analysis.
Each word was embedded using the rest of the sentence as context.
Simply put: Each word is represented as a string of numbers, but the same word does not always have the same numeric representation.
For example, the word "game" would be represented differently if it was preceded by "prisoner" versus "dictator".
As this method requires uniform input data, sentences were truncated to 512 words.
During embedding, words are broken up into constituent parts (e.g., "non-compliance" returns separate embeddings for "non" and "compliance").
We averaged embeddings of subwords within words.
This resulted in 122251 unique words, each represented by 768 numbers.

## Clustering

To cluster individual words into constructs, we used Hierarchical Density-Based Spatial Clustering of Applications with Noise (HDBSCAN).
This density-based clustering algorithm can identify clusters of varying shapes and sizes, while treating datapoints far away from any cluster as noise.
This is useful because we expect many words to be irrelevant, and only few are expected to represent theoretically relevant constructs.
Importantly, HDBSCAN performs poorly with high-dimensional data.
We therefore first used Uniform Manifold Approximation and Projection (UMAP) to reduce the original 768 dimensions to 10.
UMAP is a dimension reduction algorithm, but unlike PCA, it is non-linear and balances the preservation of the global and local structure of the data,
which has been shown to work well when clustering word vector embeddings (https://ieeexplore.ieee.org/abstract/document/9640285).
We extracted 10 dimensions, which is relatively high and thus ensures that no important information is lost.
We used cosine similarity as a distance metric, which is conventional when working with vector embeddings.
Furthermore, we specified a relatively small number of 5 neighbor points, 
which means the solution focuses more on local structure than global structure (which makes sense here, as the clusters will consist of local neighbors),
and we specified a very low minimum distance value of 0.001 to ensure that points that are close together remain very close together, which should aid subsequent clustering.
Subsequently, we performed HDBSCAN on the 10-dimensional UMAP vectors.
For HDBSCAN, we used Euclidean distance,
with a minimum cluster size of 100 words and a relatively large value of 15 for the number of surrounding datapoints needed to consider something a cluster centroid.
These values are relatively arbitrary, but their effect is that we will only obtain clusters of at least 100 words, and that clusters will be restricted to relatively dense areas.

HDBSCAN with minimum cluster size of 100 words found `r length(exmplrs)-1` clusters.
Out of `r length(df[["word"]])` words, `r tab_clust[["-1"]]` were classified as noise.
The remaining words were distributed across clusters as follows:

```{r figdist}
knitr::include_graphics(paste0("plot_dist_clust", fig_format))
```

## Construct Frequency

This is the frequency of specific constructs:

```{r figfreq}
tar_load(plot_freq_file)
knitr::include_graphics(paste0(plot_freq_file, fig_format))
```

## Co-occurrence Graph

To map the literature, a term co-occurrence matrix was computed,
which represents how frequently words occurred within the same document (see Figure \@ref(fig:tmnetworks)).
In total, there were XXX co-occurrence relationships.
To aid interpretability, small coefficients were pruned based on a negative binomial distribution,
retaining co-occurrences exceeding the $97.5^{th}$ percentile.
Note that this is a subjective criterion, which corresponded to terms that co-occurred in more than XXX documents.
After pruning, XXX co-occurrence relationships remained.

This graph illustrates which constructs co-occur within documents,
with node size weighted by construct frequency and edge linesize weighted by the frequency of co-occurrence (logarithmically scaled).

```{r fignet}
tar_load(plot_graph_file)
knitr::include_graphics(paste0(plot_graph_file, fig_format))
```


```{r fignetcircle}
tar_load(plot_graph_file)
knitr::include_graphics(paste0(plot_graph_file, "_circle", fig_format))
```

## Interactive Graph

```{r, eval = FALSE}
library(plotly)
p <- readRDS("network.rdata")
p <- p + geom_text(data = p$layers[[3]]$data, aes(x = X1, y = X2, label = name))
plotly::ggplotly(p, tooltip = "label")

```


```{r eval = TRUE, out.width="100%"}
# From ggplot
library(networkD3)
p <- readRDS("network.rdata")
nod <- p$layers[[3]]$data
nod$name <- factor(nod$name)
labs <- levels(nod$name)
nod$idnum <- as.integer(nod$name)-1L
nod$group <- "a"
edg <- p$layers[[1]]$data
edg$Source <- (as.integer(factor(edg$term1, levels = labs))-1L)
edg$Target <- (as.integer(factor(edg$term2, levels = labs))-1L)
edg$width <- scales::rescale(edg$width, to = c(1, 5))
nod <- nod[order(nod$idnum), ]
forceNetwork(Links = edg, Nodes = nod, Source = "Source", Target = "Target", NodeID = "name", zoom = TRUE, Group = "group", linkDistance = 200, 
             Value = "width", linkWidth = JS("function(d) { return d.value; }"),
             Nodesize = "size", radiusCalculation = JS("d.nodesize*1.5"),
             opacityNoHover = 1, fontSize = 20)


```

## Node Centrality

We estimated the relative importance of nodes in terms of degree centrality (the number of connections each node has) because the network structure was sparse, with just a few central constructs.

```{r}
df_plot <- read.csv("node_centrality.csv", stringsAsFactors = F)
library(ggplot2)
names(df_plot) <- c("Construct", "Frequency")
df_plot$Construct <- ordered(df_plot$Construct, levels = df_plot$Construct[order(df_plot$Frequency)])
p <- ggplot(df_plot, aes(y = Construct, x = Frequency)) +
    geom_segment(aes(x = 0, xend = Frequency,
                     y = Construct, yend = Construct
                     #, linetype = faded
    ), colour = "grey50"
    ) +
    geom_vline(xintercept = 0, colour = "grey50", linetype = 1) + xlab("Node centrality (degree)") +
    geom_point(data = df_plot, colour = "black", fill = "black", shape = 21, size = 1.5) +
    scale_x_sqrt() +
    theme_bw() + theme(panel.grid.major.x = element_blank(),
                       panel.grid.minor.x = element_blank(), axis.title.y = element_blank(),
                       legend.position = c(.70,.125),
                       legend.title = element_blank(),
                       axis.text.y = element_text(hjust=0, vjust = 0, size = 6))
p
```

## Co-occurrence as List

This figure contains the same information as the network above, but as a list so it's easier to see what the most common co-occurrence connections are:

```{r}
knitr::include_graphics(paste0("plot_cooc_freq", fig_format))
```


## Construct Details

```{r}
tar_load(exmplrs)
print(exmplrs)
```
