---
title: "CODA TMSR Report"
output: html_document
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
---

```{r setup, include=FALSE}
library(worcs)
library(dbscan)
library(umap)
library(data.table)
library(ggplot2)
library(reticulate)
library(targets)
#tar_config_set(store = "../_targets")
use_virtualenv("tmsrcoda")
knitr::opts_chunk$set(echo = FALSE)
fig_format = ".png"
```

```{r}
tar_load(df)
tar_load(exmplrs)
tar_load(res_hdbscan)
tab_clust <- table(res_hdbscan$labels)[names(exmplrs)]
```

HDBSCAN with minimum cluster size of 20 words found `r length(exmplrs)-1` clusters.
Out of `r length(df[["word"]])` words, `r tab_clust[["-1"]]` were classified as noise.
The remaining words were distributed across clusters as follows:

```{r figdist}
tar_load(plot_dist_clust_file)
knitr::include_graphics(paste0(plot_dist_clust_file, fig_format))
```

## Construct Frequency

This is the frequency of specific constructs:

```{r figfreq}
tar_load(plot_freq_file)
knitr::include_graphics(paste0(plot_freq_file, fig_format))
```

## Co-occurrence Graph

This graph illustrates which constructs co-occur within documents,
with node size weighted by construct frequency and edge linesize weighted by the frequency of co-occurrence (logarithmically scaled).

```{r fignet}
tar_load(plot_graph_file)
knitr::include_graphics(paste0(plot_graph_file, fig_format))
```

## Interactive Graph

```{r}
select_cooc <- function(cooc, q = .95){

  fit <- MASS::fitdistr(cooc, "negative binomial")
  thres <- qnbinom(q, size=fit$estimate["size"], mu=fit$estimate["mu"])
  return(cooc > thres)
}
include <- as.logical(sapply(exmplrs, `[[`, "include")[as.character(res_hdbscan$labels)])
labels <- sapply(exmplrs, `[[`, "label")[as.character(res_hdbscan$labels)]
dat <- data.frame(doc = as.integer(factor(df$doc_id)),
                  construct = res_hdbscan$labels,
                  include,
                  labels)
# Drop terms marked for exclusion
dat <- dat[dat$include, -which(names(dat)=="include")]
# Words only count once per document
dat <- dat[!duplicated(dat), ]
# Make coocurrence matrix
V <- crossprod(table(dat[1:2]))
diag(V) <- 0

df_plot <- as.data.frame.table(V)
labs <- sapply(exmplrs, `[[`, "label")[as.logical(sapply(exmplrs, `[[`, "include"))]
levels(df_plot$construct) <- labs
levels(df_plot$construct.1) <- labs
names(df_plot) <- c("term1", "term2", "cooc")
df_plot <- df_plot[as.vector(lower.tri(V)), ]

# Drop some links?
df_plot <- suppressWarnings(df_plot[select_cooc(df_plot$cooc), ])
# Create network ----------------------------------------------------------
cluster_freq <- read.csv("cluster_freq.csv", stringsAsFactors = FALSE)
edg <- df_plot
names(edg) <- c("source", "target", "width")

vert <- data.frame(name = as.character(unique(unlist(edg[1:2]))))
vert$size <- cluster_freq$Frequency[match(vert$name, cluster_freq$Construct)]
vert$size <- scales::rescale(log(vert$size), c(4, 12))
library(igraph)
library(networkD3)
g <- graph_from_data_frame(edg, vertices = vert, directed = FALSE)

netd3 <- igraph_to_networkD3(g)
lnk <- netd3$links
nod <- netd3$nodes
nod$group <- "group1"

forceNetwork(Links = lnk, Nodes = nod, Source = "source", Target = "target", NodeID = "name", zoom = TRUE, Group = "group", linkDistance = 200)
```


## Construct Details

```{r}
tar_load(exmplrs)
print(exmplrs)
```
